%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Medium Length Professional CV
% LaTeX Template
% Version 2.0 (8/5/13)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Rishi Shah
%
% Important note:
% This template requires the resume.cls file to be in the same directory as the
% .tex file. The resume.cls file provides the resume style used for structuring the
% document.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass{resume}

\usepackage[left=1in,top=0.5in,right=0.5in,bottom=1in]{geometry}
\usepackage{multicol}
\usepackage{amsmath,amsfonts,amsthm,amssymb,mathtools,hyperref,mathrsfs}

\usepackage{listings} % for placeholder images
\lstdefinestyle{mystyle}{
  commentstyle=\color{codegreen},
  keywordstyle=\color{magenta},
  numberstyle=\tiny\color{codegray},
  stringstyle=\color{codepurple},
  basicstyle=\ttfamily,
  breakatwhitespace=false,
  breaklines=true,
  captionpos=b,
  keepspaces=true,
  numbers=left,
  numbersep=5pt,
  showspaces=false,
  showstringspaces=false,
  showtabs=false,
  tabsize=2
}
\lstset{style=mystyle}
\AtBeginEnvironment{tabular}{\ttfamily}

\name{Alec S. Zabel-Mena}
\address{
  alec.zabel@upr.edu \\
  azabelmena.github.io  \\
  github.com/azabelmena
}

\begin{document}

\begin{rSection}{Education}
  \textbf{Universtiy of Puerto Rico}, at R\'io Piedras
  \hfill August $2022$ -- December $2025$ (Expected)  \\
  \textit{Master of Science in Pure Mathematics} \\

  \textbf{Universtiy of Puerto Rico}, at R\'io Piedras
  \hfill August $2016$ -- June $2022$  \\
  \textit{Bachelor of Science in Pure Mathematics}  \\
  \textit{Minor in Cybersecurity}
\end{rSection}

\begin{rSection}{Career Objective}
  To become an academic researcher and professor. Aiming to research both pure
  and applied mathematics; specifically research in algebraic
  geometry, coding theory, and other areas of discrete mathematics.
\end{rSection}

\begin{rSection}{Research Interests}
  \begin{multicols}{2}
    \begin{itemize}
      \item Commutative Algebra

      \item Algebraic Geometry

      \item Finite Fields

      \item Graph theory, and Combinatorics

      \item Matroid theory

      \item Category Theory and Homotopy Type Theory
    \end{itemize}
  \end{multicols}
\end{rSection}


\begin{rSection}{Publications}
  \begin{enumerate}
    \item Agrinsoni, C.A., Janwa, H., \textit{Zabel-Mena, A.S.}
      \textit{Absolute Irreducibility of Generalized
        Trinomials Defined by APN Functions of The Form
      $g(x)=2^{2^ie}+h(x)$ over $\mathbb{F}_{2^s}$}. Springer
      Proceedings in Mathematics \& Statistics, (To be submitted).
      $2025$.
  \end{enumerate}
\end{rSection}

\begin{rSection}{Presented Works}
  \begin{enumerate}
    \item \textit{Zabel-Mena, A.S.}, Janwa, H. Agrinsoni, C.A.
      \textit{Absolute Irreducibility of Generalized
        Trinomials Defined by APN Functions of The Form
      $g(x)=2^{i}+h(x)$ over $\mathbb{F}_{2^s}$} (Contributed Talk).
      $40$\textsuperscript{th} Seminario Interuniversitario de
      Investigaci\'on en Ciencias Matem\'aticas (SIDIM), Ponce P.R.
      $2025$.

    \item \textit{Zabel-Mena, A.S.}, Janwa, H. Agrinsoni, C.A.
      \textit{An Efficient Implementation and Analysis Of Zeta
      Functions Of APN Curves and Their Protograph LDPC Codes}
      (Contributed Talk). $39$\textsuperscript{th} Seminario
      Interuniversitario de Investigaci\'on en Ciencias Matem\'aticas
      (SIDIM), Humacao P.R. $2024$.

    \item \textit{Zabel-Mena, A.S.}, Janwa, H. Agrinsoni, C.A.
      \textit{An Efficient Implementation and Analysis Of Zeta
      Functions Of APN Curves and Their Protograph LDPC Codes}
      (Poster Session). Forward Research and Innovation Summit, San
      Juan P.R. $2023$.
  \end{enumerate}
\end{rSection}

\begin{rSection}{Grants and Awards}
  \textbf{PR Space Grant Fellowship and Scholarship Program}, NASA
  \hfill{August $2024$ -- May $2025$} \\
  Grant No. 80NSSC20M0052 \\

  \textbf{Research Assitantship}, NASA
  \hfill{January $2024$ -- May $2024$} \\
  Grant No. 80NSSC20M0052 \\

  \textbf{Research Assitantship}, NASA
  \hfill{August $2023$ -- December $2023$} \\
  Grant No. 80NSSC20M0052 \\

  \textbf{PR Space Grant Fellowship and Scholarship Program}, NASA
  \hfill{August $2022$ -- May $2023$} \\
  Grant No. 80NSSC20M0052 \\
\end{rSection}

\begin{rSection}{Teaching and Mentoring}
  \textbf{Proyecto Tutor\'ias DECEP} \hfill{2020-2021} \\
  University of Puerto Rico, R\'io Piedras \\
  Mathematics tutor
  \begin{itemize}
    \item[] Conducted assessments to identify the educational needs of my
      students and developed individualized learning plans.

    \item[] Tasked with providing tutoring services to seven high school
      students for $10$ hours a week in the subjects of Algebra and
      Pre-Calculus.
  \end{itemize}

  \textbf{Self-Employed} \hfill{2019-2021} \\
  Mathematics tutor

  \begin{itemize}
    \item[] Evaluated students learning styles and provided appropriate
      techniques for maximizing understanding and minimizing frustration.

    \item[] Simplified math concepts while coaching students to think
      critically when problem solving; eventually introducing them to
      axiomatic systems within mathematics.

    \item[] Provided tutoring one-on-one to five highschool students in the
      subjects of Algebra, Pre-Calculus, and Geometry for two times a
      week, at two hours for each session.
  \end{itemize}
\end{rSection}

\begin{rSection}{Memberships and Affiliations}
  \textbf{Consejo General de Estudiantes} (UPRRP)
            \hfill August $2024$ -- May $2025$  \\
  Representante ante el Consejo de Estudios Graduados e
  Investigaci\'on \\

  \textbf{Consejo de Estudiantes de Ciencias Naturales} (UPRRP)
            \hfill August $2024$ -- May $2025$  \\
  Representante ante el Decanato de Estudios Graduados e
  Investigaci\'on \\
  {\footnotesize Resigned from post}.  \\

  \textbf{Asociaci\'on Estudiantil de Matem\'aticas} (AeMAT)
            \hfill August $2019$ -- Present \\
    Treasurer \hfill August $2025$ -- May $2026$ \\
    {\footnotesize Post yet to be assumed}.  \medskip \\
    Treasurer \hfill August $2022$ -- May $2024$ \\

  \textbf{Asociaci\'on de Estudiantes de Ciencias de Computos} (AECC)
            \hfill August $2025$ -- May  $2026$ \\

  \textbf{Lembran\c{c}a Negra Capoeira} \hfill $2017$ -- $2019$ \\
  Corda Crua-Verde  \\

  \textbf{Senzala Capoeira} (Sou Capoeira) \hfill $2019$ -- Present \\
  Corda Crua-Laranja  \\
\end{rSection}

\begin{rSection}{Skills}
  \textbf{Languages}
  \begin{itemize}
    \item[] English

    \item[] Spanish

    \item[] Portuguese
  \end{itemize}

  \textbf{Software}
  \begin{itemize}
    \item[] \LaTeX

    \item[] \lstinline{C} programming

    \item[] \lstinline{SAGE} Mathematics Software

    \item[] \lstinline{nix}
  \end{itemize}
\end{rSection}

\end{document}
